Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants\thanks{Supported by EPSRC grant EP/J012564/1, ERC project 280053 (CPROVER) and the H2020 FET OPEN 712689 SC$^2$.}

### 2017-05-01 cav2017/cav2017.tex
wording

Linear Time Invariant (LTI) models represent a broad class of dynamical
systems with significant impact in numerous application areas as in the life
sciences, robotics, and engineering~\cite{astrom1997computer,Franklin15}. 
Synthesis of controllers for LTI models is broadly investigated, however the
use of digital control architectures adds new challenges due to the effects
of finite-precision arithmetic, time discretization, and quantization noise,
which are typically introduced by Analogue-to-Digital (ADC) and
Digital-to-Analogue (DAC) conversion.  While research on digital control is
well developed~\cite{astrom1997computer}, automated and sound control
synthesis is challenging, particularly when the synthesis objective goes
beyond classical stability.  There are recent methods for verifying more
general reachability properties of a given controller~\cite{FLD+11,Fre05}. 
However, these methods have not been generalized to control synthesis. 
We~remark that a synthesis algorithm that guarantees satability does not
ensure safety: the system might transitively visit an unsafe state that
results in an unrecoverable failure.

>>>>

Linear Time Invariant (LTI) models represent a broad class of dynamical
systems with significant impact in numerous application areas such as in life
sciences, robotics, and engineering~\cite{astrom1997computer,Franklin15}. 
Synthesis of controllers for LTI models is broadly investigated, however the
use of digital control architectures adds new challenges due to the effects
of finite-precision arithmetic, time discretization, and quantization noise,
which are typically introduced by Analogue-to-Digital (ADC) and
Digital-to-Analogue (DAC) conversion.  While research on digital control is
well developed~\cite{astrom1997computer}, automated and sound control
synthesis is challenging, particularly when the synthesis objective goes
beyond classical stability.  There are recent methods for verifying more
general reachability properties of a given controller~\cite{FLD+11,Fre05}. 
However, these methods have not been generalized to control synthesis. 
We~remark that a synthesis algorithm that guarantees satability does not
ensure safety: the system might transitively visit an unsafe state that
results in an unrecoverable failure.
